Rough Draft

### 2017-11-01 Article submission/roughdraft.tex
edits

Community-driven online question and answer forums (CQA) are becoming increasingly valuable sources of information. These platforms house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday. There are forums that cover a broad range of topics, like Yahoo! Answers, and forums focused on specific topics, like computer programming-focused Stack Overflow. An example of the latter is iFixit's CQA, Answers. As the main goal of iFixit is to teach people to fix their own devices by providing them with the knowledge and tools necessary, Answers---featuring questions related specifically to device repair---is a valuable source of information for this community. Thus, it's important that questions receive answers, and receive them quickly. This paper presents a survival analysis on the time until a question recieves its first answer. We developed a cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time. Though our model was signficant, its predictive accuracy was low. Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products receiving answers faster than others), and factors related to the question's title (e.g., whether or not it's phrased as a question, or if it contains terms considered ``unpopular''). For future studies, our findings can be applied to other models and further analysis of answer times in CQA.

@@

    The CQA analyzed in this paper is iFixit's Answers forum. iFixit is a company founded in 2003 by two engineering students of the California Polytechnic State University in San Luis Obispo. What began as a business running out of the college dorms, is now a company that helps thousands of people fix their broken devices everyday, providing over 30,000 free repair guides with pictures and step-by-step instructions. iFixit also sells the specialized tools and parts needed for such repairs---tools like iPhone 7 battery adhesive strips or a Nexus 9 LCD digitizers. The main goal of this company is to provide people with the help and tools they might need to repair their devices, and in teaching people how to extend the lifetime of their devices, it allows people to save money and cut down on electronic waste.

    Along with repair guides and tool sales, another important component of this company is the online question and answer forum, Answers. This platform features questions related to device repair, featuring over 9,000 devices and over 100,000 solutions and answers. Questions on this forum range from broken devices like a jammed zippers to shattered iPhone screens. This forum is an integral part in teaching people how to fix their own devices. If people run into problems, they can always trust that they have a large community to turn to for help. Thus it's important, for both the individuals as well as iFixit, that askers get prompt answers. Fast response times will drive up user engagement and generate more traffic, which in turn is great for the reputation and longevity of Answers and iFixit. As such, investigation of response times would be both beneficial and informative. Analysis can reveal factors within the forum and from elements of the questions, that affect how quickly questions get answers. Suggestions for how users can ask questions to minimize answer times and for how the forum design can be improved, can be derived from such analysis.

    However, to the best of our knowledge, analysis and prediction of answer times on forums has not been investigated by many researchers. A majority of the research focuses on assessing and predicting the question and answer quality. As such, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's Answers forum. It attempts to determine the factors that are significantly related to answer time, and create a cox proportional hazards model that can accurately predict the failure probability of a question.

@@

    The data analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017, the date the data was downloaded. We worked exclusively with questions in English. Of the questions in the data set, 4,951, or 63.8\%, recieved an answer. Questions that remained unanswered were considered right-censored. The time until event variable used in survival analysis methods was defined as the time until a question posted on the forum recieves an answer. Comments posted on the question are not considered answers, and an answer does not have to be accepted as the ``chosen solution'' to be considered the answer. We are only considering the time until the question recieves its first answer. The time until answer value for right-censored questions, questions that did not recieve an answer, is defined as the time from when the question was posted, to the time the data was downloaded. Figure a shows the distribution of answer times for all questions in the data set.

    The following statistics were calculated from Kaplan-Meier estimates of survival probabilities for each question in the data. As Kaplan-Meier estimates adjust for the presence of censored observations, these statistics are adjusted for the presence of unanswered questions. In this analysis, survival is defined as the event that a question remains unanswered beyond a certain time, t. For questions in this data set, the mean survival time, or the average time until a question recieves its first answer is 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data recieved an answer is 9.16 hours. Table 1 provides more percentiles of survival time. 
    Figure A shows the Kaplan-Meier Curve for all questions in the data. The curve indicates that around 100 hours, the probability that a question recieves an answer after that time hovers around 0.35. The survival probability never reaches 0 due to the large amount of unanswered questions.

@@

    The data contained information about each question's title, text, and device, from which we created the following variables to use in the cox regression model.

The time until a question recieves its first answer, as described above, was calculated as the time from the time the question was posted to the time the first answer was received in hours. If the question did not receive an answer, the time until answer value was calculated as the time from when the question was posted, to the time the data was downloaded, July 7, 2017 at 2:41 PM PDT. The censoring variable indicates 1 if the question received an answer, and 0 if the question remained unanswered by the time the data set was downloaded.

@@

\begin{itemize}
  \item Questions were categorized based off of the devices it pertains to. Categories include: Apple Products, Android\/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, Other. Home, Vehicle, Other. Table B shows the percentage of questions within each device category. 
  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions.
  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. 
  \item Whether or not the question's title ends in a question mark.
  \item Whether or not the question's title begins with a "Wh" word (e.g. "What", "Where"). 
  \item Whether or not the question's text contains any end punctuation marks (. ? !). 
  \item Whether or not the question's text is in all lower case. 
  \item Whether or not the asker updated the question's text (e.g., edited or added information) sometime after posting it. 
  \item Whether or not the asker included a greeting (e.g. ``Hello'', ``Greetings'') in the question's text.
  \item Whether or not the asker used polite language in the question's text (e.g., ``Thank you'', ``please''). 
  \item Whether or not the asker made an effort to solve the problem on their own, prior to asking the question.
  \item The day of the week the question was posted. 
  \item The time of day the question was posted. Times include: Morning, Afternoon, Evening, and Night. 
\end{itemize}

@@

5-fold cross-validation was used to assess predictive performance. Training data sets contained 6,208 questions. Test data sets contained 1,552 questions.

For each iteration of cross-validation, the model fit to the training data was used to calculate predicted hazard ratios from the corresponding test data. To assess prediction performance, those predicted ratios were entered into a separate cox regression model as the explanatory variable with the question's answer times as the survival time value. The resulting hazard ratio, R-square statistic, partial likelihood ratio and p-value, Somers' Dxy and Concordance statistic for that model were used as indicators of the prediction model's performance. If this model gave significant results, this would indicate that the predicted hazard ratio is signficantly associated with survival time, and that our prediction model performs well. Somers' Dxy and Concordance statistics are measures of how well the model can rank predictions. (add to this) The concept behind these metrics came from \cite{Chen}. These metrics were also computed for predictions on the training data itself. For each of the five iterations, there was no signficant difference between the metrics computed on the training data predictions, and the metrics computed on the test data. Table C shows average metrics for training and test data predictions. The metrics taken into consideration was the average of all metrics computed on test data. Although these metrics are not considerably high, they do not vary signicantly from training to test data sets.

@@

The final model, including all variables described above, was fit to the full data set.
The proportional hazards assumption was assessed by using the cox.zph function of the survival package in R (expand on this, don't mention function name). This test is based on the correlation between scaled Schoenfeld residuals and a function of time. Signficant p-values of this test indicate a possible violation of the proportional hazard assumption. For our model, the ``Apple Product'' level of the device category variable had the lowest p-value of 0.01. The next lowest p-values hovered around 0.04, for variables like device\_length, and the Camera and Game Console levels of category. As Apple Product was the only major violation of this assumption, and stratifying on this variable substantially decreased the predictive power, this assumption was considered to be fine (rewrite this).

Assessing the martingale residuals for each quantitative predictor indicated that the functional form appears to be adequate. Assessing the deviance residuals indicated that a considerable amount of questions were not predicted well by the model. Assessing the score residuals showed that some questions might have a strong influence on the fit of the model. However, in both cases, fitting the model without such questions resulted in worse predicted performance.

@@

\begin{itemize}
  \item Stratification on the time of day the question was posted. 
  \item Square root of the average frequency of a question's tags. 
  \item Quadratic polynomial on the length of the question's text. 
  \item Restricted cubic splines on the number of characters in the device name, the average length of a question's tags, and the ratio of newlines to number of characters in a question's text. Knots assigned to these variables were 5, 4, 4, respectively. 
\end{itemize}

The final model gave an AIC value of 69945.32. The partial loglikelihood ratio test statistic was 1307.15 with a p-value of 0. The R-squared value for this model is 0.1555. Variables that proved to be significant predictors with a p-value of less than 0.01 are: new_category (apple product, camera, game console, home, pc, and vehical), contain_unanswered, title_quesitonmark, update, prior_effort, avg_tag_score and the spline on avg_tag_length. Include some interpretations of the hazard ratio?

While the model is significant overall, the metrics for the model's predictive accuracy are not impressive. This indicates that perhaps a different model might perform better in predicting the answer times for questions. Another suggestion is that a model with more quantitative variables might perform better as well.

>>>>

Community-driven online question and answer forums (CQA) are becoming increasingly valuable sources of information. These platforms house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday. There are forums that cover a broad range of topics, like Yahoo! Answers, and forums focused on specific topics, like computer programming-focused Stack Overflow. An example of the latter is iFixit's Answers forum. As the main goal of iFixit is to enable people to fix their own devices by providing them with the knowledge and tools necessary, the Answers forum, which features questions related specifically to device repair, is a valuable source of information for this community. Thus, it is important that questions receive timely answers. This paper presents a survival analysis on the time until a question receives its first answer. We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time. Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = 0.15$). Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.

@@

    The CQA analyzed in this paper is iFixit's Answers forum. Founded in 2003 by two engineering students at the California Polytechnic State University in San Luis Obispo, iFixit now helps thousands of people repair their broken devices everyday. The company provides over 30,000 free online repair guides with pictures and step-by-step instructions, and sells the specialized tools and parts needed for such repairs---tools like iPhone 7 battery adhesive strips or Nexus 9 LCD digitizers. The main goal of this company is to enable people to extend the lifetime of their own devices, effectively saving them money and reducing electronic waste.

    As the goal of this company is to provide people with the knowledge necessary to repair their devices, an important part of this company is their CQA, called Answers. This platform features questions related specifically to device repair, with over 9,000 device topics and over 100,000 solutions. As many rely on this forum and the community of people who provide answers, for help with their own device repairs, it's important that these users receive timely answers. Fast response times will drive up user engagement and generate more traffic, which in turn is great for the reputation and longevity of the Answers forum. As such, investigation of response times would be both beneficial and informative. Analysis can reveal factors within the forum and from elements of the questions that affect how quickly questions are answered. Suggestions for how users can ask questions to minimize answer times and for how the forum design can be improved, can be derived from such analysis.

    However, to the best of our knowledge, analysis and prediction of answer times on CQAs have not been thoroughly investigated. A majority of the existing research focuses on assessing and predicting question and answer quality. As such, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's Answers forum. It attempts to determine the factors that are significantly related to answer time, and create a cox proportional hazards model that can accurately predict the failure probability of a question.

@@

    The data analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017, the date the data was downloaded. We worked exclusively with questions in English. Of the questions in the data set, 4,951, or 63.8\%, recieved an answer. Questions that remained unanswered were considered right-censored. The time until event variable used in survival analysis methods was defined as the time until a question posted on the forum receives an answer. Comments posted on the question are not considered answers, and an answer does not have to be accepted as the ``chosen solution'' to be considered the answer. We are only considering the time until the question receives its first answer. The time until answer value for right-censored questions, questions that did not receive an answer, is defined as the time from when the question was posted, to the time the data was downloaded. Figure a shows the distribution of these answer times for all questions in the data set.

    The following statistics were calculated from Kaplan-Meier estimates of questions survival probability. In this analysis, survival is defined as the event that a question remains unanswered beyond a certain time, t. As Kaplan-Meier estimates adjust for the presence of censored observations, these statistics are adjusted for the presence of unanswered questions. For questions in this data set, the mean survival time, or the average time until a question receives its first answer is 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer is 9.16 hours. Table 1 provides more percentiles of survival time. 
    Figure A shows the Kaplan-Meier Curve for all questions in the data. The curve indicates that around 100 hours after question is posted, the probability that a question receives an answer after that time hovers around 0.35. The survival probability never reaches 0 due to the large amount of unanswered questions.

@@

    The data contained information about each question's title, text, and device, from which we created the following variables to use in the Cox regression model.

The time until a question receives its first answer was calculated as the time, in hours, from the time the question was posted to the time the first answer was received. If the question did not receive an answer, the time until answer value was calculated as the time from when the question was posted, to the time the data was downloaded, July 7, 2017 at 2:41 PM PDT. The censoring variable indicates 1 if the question received an answer, and 0 if the question remained unanswered.

@@

\begin{itemize}
  \item Device category the question pertains to. Categories include: Apple Products, Android\/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, Other. Table B shows the percentage of questions within each device category. 
  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions.
  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. 
  \item Whether or not the question's title ends in a question mark.
  \item Whether or not the question's title begins with a ``Wh'' word (e.g. ``What'', ``Where''). 
  \item Whether or not the question's text contains any end punctuation marks (. ? !). 
  \item Whether or not the question's text is in all lower case. 
  \item Whether or not the asker edited or added information to the questions text sometime after posting it. 
  \item Whether or not the asker included a greeting (e.g. ``Hello'', ``Greetings'') in the question's text.
  \item Whether or not the asker used polite language in the question's text (e.g., ``Thank you'', ``please''). (don't like the way this is worded) 
  \item Whether or not the asker made an effort to solve the problem on their own, prior to asking the question.
  \item The day of the week the question was posted. 
  \item The time of day the question was posted. Times include: Morning, Afternoon, Evening, and Night. 
\end{itemize}

@@

5-fold cross-validation was used to assess predictive performance. Training data sets contained 6,208 questions. Test data sets contained 1,552 questions. For each iteration, the model fit to the training data was used to calculate predicted hazard ratios from the corresponding test data. To assess prediction performance, those predicted hazard ratios were entered into a separate Cox regression model as the single predictor with the question's answer times as the survival time. The resulting hazard ratio, R-square statistic, partial likelihood ratio and p-value, Somers' Dxy and Concordance statistics for that model were used as indicators of the prediction model's performance. Significant statistics for this model would indicate that the predicted hazard ratio is signficantly associated with survival time and that our modle performs well. The concept behind these metrics came from \cite{Chen}. These metrics were also computed for predictions on the training data. For each of the five iterations, there was no signficant difference between the metrics computed on the training data prediction, and the metrics computed ont he test data. Table C shows the average metrics for training and test data predictions. The metrics evaluated were the average of all metrics computed on the test data. Although these metrics are not considerably high, they do not vary signicantly from training to test data sets.  (should I explain more about Somers' Dxy and Concordance?)

@@

@@

\begin{itemize}
  \item Stratification on the time of day the question was posted. 
  \item Square root of the average frequency of a question's tags. 
  \item Quadratic polynomial on the length of the question's text. 
  \item Restricted cubic spline with 5 knots on the number of characters in the device name.
  \item Restricted cubic spline with 4 knots on the average number of characters in a question's tags.
  \item Restricted cubic spline with 4 knots on the ratio of newlines to the number of characters in a question's text. 
\end{itemize}

Assessing the indepenedence between the model's Schoenfeld residuals and time indicated that the ``Apple Product'' category of the device variable violated the proportional hazards assumption. Other variables at risk for violation included the Camera and Game Console categories of devices, and the number of characters in the user-defined device name. As ``Apple Product'' was the only major violation of this assumption, and stratifying on this variable substantially decreased predictive power, these variables were left as is. 
Visually assessing martingale residuals for each quantitative predictor indicated that functional form for each appeared to be adequate. Assessing the deviance residuals indicated that a considerable amount of questions were not predicted well by the model. Similarily, assessing the score residuals showed that some questions might have an influence on the fit of the model. However, fitting the model without questions identified by score and deviance residuals to be either poorly predicted or highly influential, resulted in worse predictive performance. Hence, all questions were left in the data set.

The partial likelihood ratio test statistic was 1307.15 with a p-value of 0. The R-squared value for this model is 0.1555. Significant predictors with a p-value of less than 0.01 are: the Apple product, Camera, Game Console, Home, PC, and Vehicle categories of the device variable, whether or not the question's text contained at least one term considered ``frequently used'' among answered questions, whether or not question's title ended in question mark, whether or not the asker edited the question's text after posting, whether or not the asker made effort prior to posting the question to find their own solution, the average frequency of a question's tags, and average number of characters for a question's tags. Include some interpretations of the hazard ratio?

While the model is significant overall, it's predictive accuracy is low. Table blah shows metrics for the model fit to the full data set. One possible explanation for this is the high number of categorical variables included in the model. Including more quantitative variables may improve predictive accuracy. 
The data we analyzed for this model presented some limitations. Currently, askers have a considerable amount of freedom in the way they ask a question. As a result many have incorrectly specified various input fields when asking their question. For example, a question about a faulty Android tablet screen included as a tag ``someone sat on it :(''. Generally, tags are not more than a couple key words that describe the topic of the question. Many askers on this forum included lengthy and somewhat ambiguous tags in their question. Another issue was the incorrect naming of the device the asker's question was about. A user asking a question about their Turtle Beach Ear Force X device included as the name of their device "Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One". The inconsistencies in this data made it somewhat difficult to analyze, and possibly contributes to the model's low predictive accuracy.

\section{Conclusion}
